Score-based tests of measurement invariance: Use in practice

### 2013-10-25 frontiers/frontiers.Rnw
fix Fig9(right now Fig10) problem and add one figure in Appendix to show all loading and all errors.
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/semtools@283 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\begin{figure}
\caption{Simulated power curves for $\max \mathit{LM}_o$, $\mathit{WDM}_o$, and
$\mathit{LM}_{uo}$ across three levels of the ordinal variable $m$,
  and measurement invariance 
violations of 0--4 standard errors (scaled by $\sqrt{n}$). The
parameter violating measurement invariance is $\phi_{12}$.}
\label{fig:sim12res}
<<sim12res, fig=TRUE, height=4, width=9, echo=FALSE>>=
trellis.par.set(theme = canonical.theme(color = FALSE))
mykey <- simpleKey(levels(sim1$test), points = TRUE, lines = TRUE)
xyplot(power ~ diff | nlevels, group = ~ test, data = sim1,
       subset = (parms == "var" & 
		 pars %in% c("Covariance") & diff %% 0.5 == 0),
       type = "b", xlab = "Violation Magnitude", ylab="Power", key = mykey, as.table = TRUE,
       strip = function(..., which.given, factor.levels){
	   if(which.given == 2){
	       strip.default(which.given, factor.levels = parlabs[c(2)],...)
	   } else {
	       strip.default(which.given, factor.levels = factor.levels, ...)
	   }
       })
@

@@

\subsection{Results}
Results of
primary interest are conditions where the unmodeled loading violates
measurement invariance.  These results are displayed in Figure~\ref{fig:sim21res}.  One can generally observe
that tests of the first loading and unique variance exhibited high
``power,'' which is actually a high Type I error rate here.  Tests
associated with the factor 
covariance (not shown) did not demonstrate this error, however. In
terms of specific 
statistic performance, $\max \mathit{LM}_o$ and $\mathit{WDM}_o$ 
demonstrated higher Type I error than $\mathit{LM}_{uo}$ in each panel,
especially with increasing levels.  This is likely because the unmodeled
loading's non-invariance was monotonic with $V$; if it were not monotonic, we
would expect $\mathit{LM}_{uo}$ to have higher Type I error.

@@

This Appendix contains results for Simulation 2, where there existed
model misspecification (lacking one loading from Scale 1 to
Math). Figure~\ref{fig:sim22res} to Figure~\ref{fig:sim24res} display
results when the loading $\lambda_{11}$, covariance $\phi_{12}$, and  
error term $\psi_{11}$ violate invariance, respectively.

\begin{figure}
\caption{Simulated power curves for $\max \mathit{LM}_o$, $\mathit{WDM}_o$, and $\mathit{LM}_{uo}$ across three levels of the ordinal variable $m$ and measurement invariance 
violations of 0--4 standard errors (scaled by $\sqrt{n}$). The
parameter violating measurement invariance is $\lambda_{11}$.  Panel
labels denote the parameter(s)  
being tested (top) and levels of the ordinal variable $m$ (bottom).}
\label{fig:sim22res}
<<sim22res, fig=TRUE, height=7, width=9, echo=FALSE>>=
trellis.par.set(theme = canonical.theme(color = FALSE))
mykey <- simpleKey(levels(sim2$test), points = TRUE, lines = TRUE)
xyplot(power ~ diff | nlevels + pars, group = ~ test, data = sim2,
       subset = (parms=="extra+loading" & 
		 pars %in% c("Loading1", "All Loadings") & diff %% 0.5 == 0),
       type = "b", xlab = "Violation Magnitude", ylab = "Power", key = mykey, as.table = TRUE,
       strip = function(..., which.given, factor.levels){
	   if(which.given == 2){
	       strip.default(which.given, factor.levels = parlabs[c(1, 4)], ...)
	   } else {
	       strip.default(which.given, factor.levels = factor.levels, ...)
	   }
       })
@

@@

\begin{figure}
\caption{Simulated power curves for $\max \mathit{LM}_o$, $\mathit{WDM}_o$, and $\mathit{LM}_{uo}$ across three levels of the ordinal variable $m$ and measurement invariance 
violations of 0--4 standard errors (scaled by $\sqrt{n}$). The
parameter violating measurement invariance is $\phi_{12}$.  Panel
labels denote the parameter(s)  
being tested (top) and levels of the ordinal variable $m$ (bottom).}
\label{fig:sim23res}
<<sim23res, fig=TRUE, height=4, width=9, echo=FALSE>>=
trellis.par.set(theme = canonical.theme(color = FALSE))
mykey <- simpleKey(levels(sim2$test), points = TRUE, lines = TRUE)
xyplot(power ~ diff | nlevels, group = ~ test, data = sim2,
       subset = (parms=="extra+var" & 
		 pars %in% c("Covariance") & diff %% 0.5 == 0),
       type = "b", xlab = "Violation Magnitude", ylab = "Power", key = mykey, as.table = TRUE,
       strip = function(..., which.given, factor.levels){
	   if(which.given == 2){
	       strip.default(which.given, factor.levels = parlabs[c(2, 4:5)], ...)
	   } else {
	       strip.default(which.given, factor.levels = factor.levels, ...)
	   }
       })
@

@@

\begin{figure}
\caption{Simulated power curves for $\max \mathit{LM}_o$, $\mathit{WDM}_o$, and $\mathit{LM}_{uo}$ across three levels of the ordinal variable $m$ and measurement invariance 
violations of 0--4 standard errors (scaled by $\sqrt{n}$). The
parameter violating measurement invariance is $\psi_{11}$.  Panel
labels denote the parameter(s)  
being tested (top) and levels of the ordinal variable $m$ (bottom).}
\label{fig:sim24res}
<<sim24res, fig=TRUE, height=9, width=9, echo=FALSE>>=
trellis.par.set(theme = canonical.theme(color = FALSE))
mykey <- simpleKey(levels(sim2$test), points = TRUE, lines = TRUE)
xyplot(power ~ diff | nlevels + pars, group = ~ test, data = sim2,
       subset = (parms == "extra" & 
		 pars %in% c("Error1", "All Errors", "All Loadings") & diff %% 0.5 == 0),
       type = "b", xlab = "Violation Magnitude", ylab = "Power", key = mykey, as.table = TRUE,
       strip = function(..., which.given, factor.levels){
	   if(which.given == 2){
	       strip.default(which.given, factor.levels = parlabs[c(3, 4:5)], ...)
	   } else {
	       strip.default(which.given, factor.levels = factor.levels, ...)
	   }
       })
@

>>>>

\begin{figure}
\caption{Simulated power curves for $\max \mathit{LM}_o$, $\mathit{WDM}_o$, and
$\mathit{LM}_{uo}$ across three levels of the ordinal variable $m$,
  and measurement invariance 
violations of 0--4 standard errors (scaled by $\sqrt{n}$). The
parameter violating measurement invariance is $\phi_{12}$. Panel
labels denote the parameter(s)  
being tested (top) and levels of the ordinal variable $m$ (bottom).}
\label{fig:sim12res}
<<sim12res, fig=TRUE, height=4, width=9, echo=FALSE>>=
trellis.par.set(theme = canonical.theme(color = FALSE))
mykey <- simpleKey(levels(sim1$test), points = TRUE, lines = TRUE)
xyplot(power ~ diff | nlevels, group = ~ test, data = sim1,
       subset = (parms == "var" & 
		 pars %in% c("Covariance") & diff %% 0.5 == 0),
       type = "b", xlab = "Violation Magnitude", ylab="Power", key = mykey, as.table = TRUE,
       strip = function(..., which.given, factor.levels){
	   if(which.given == 2){
	       strip.default(which.given, factor.levels = parlabs[c(2)],...)
	   } else {
	       strip.default(which.given, factor.levels = factor.levels, ...)
	   }
       })
@

@@

\subsection{Results}
Results of
primary interest are conditions where the unmodeled loading violates
measurement invariance.  These results are displayed in Figure~\ref{fig:sim21res}.  One can generally observe
that tests of the first loading and unique variance exhibited high
``power,'' which is actually a high Type I error rate here.  This Type I error also demonstrated when testing all loadings and all unique variances.  The result is shown in Appendix.\seeme{From ''This type I'' to ''Appendix'' are added to refer to the added Appendix Figure. }  Tests
associated with the factor 
covariance (not shown) did not demonstrate this error, however. In
terms of specific 
statistic performance, $\max \mathit{LM}_o$ and $\mathit{WDM}_o$ 
demonstrated higher Type I error than $\mathit{LM}_{uo}$ in each panel,
especially with increasing levels.  This is likely because the unmodeled
loading's non-invariance was monotonic with $V$; if it were not monotonic, we
would expect $\mathit{LM}_{uo}$ to have higher Type I error.

@@

This Appendix contains results for Simulation 2, where there existed
model misspecification (lacking one loading from Scale 1 to
Math). Figure~\ref{fig:sim22res} to Figure~\ref{fig:sim25res} display
results when the unmodeled loading\seeme{add this to refer to the added figure}, loading $\lambda_{11}$, covariance $\phi_{12}$, and  
error term $\psi_{11}$ violate invariance, respectively.

\begin{figure}
\caption{Simulated power curves for $\max \mathit{LM}_o$, $\mathit{WDM}_o$, and $\mathit{LM}_{uo}$ across three levels of the ordinal variable $m$ and measurement invariance 
violations of 0--4 standard errors (scaled by $\sqrt{n}$). The
parameter violating measurement invariance is the unmodeled
loading. Panel labels denote the parameter(s) 
being tested (top) and levels of the ordinal variable $m$ (bottom).}
\label{fig:sim22res}
<<sim22res, fig=TRUE, height=7, width=9, echo=FALSE>>=
trellis.par.set(theme = canonical.theme(color = FALSE))
mykey <- simpleKey(levels(sim2$test), points = TRUE, lines = TRUE)
xyplot(power ~ diff | nlevels + pars, group = ~ test, data = sim2,
       subset = (parms == "extra" & 
		 pars %in% c("All Loadings", "All Errors") & diff %% 0.5 == 0),
       type = "b", xlab = "Violation Magnitude", ylab = "Power", key = mykey, as.table = TRUE,
       strip = function(..., which.given, factor.levels){
	   if(which.given == 2){
	       strip.default(which.given, factor.levels = parlabs[c(4, 5)], ...)
	   } else {
	       strip.default(which.given, factor.levels = factor.levels, ...)
	   }
       })
@

@@

\begin{figure}
\caption{Simulated power curves for $\max \mathit{LM}_o$, $\mathit{WDM}_o$, and $\mathit{LM}_{uo}$ across three levels of the ordinal variable $m$ and measurement invariance 
violations of 0--4 standard errors (scaled by $\sqrt{n}$). The
parameter violating measurement invariance is $\lambda_{11}$.  Panel
labels denote the parameter(s)  
being tested (top) and levels of the ordinal variable $m$ (bottom).}
\label{fig:sim23res}
<<sim23res, fig=TRUE, height=7, width=9, echo=FALSE>>=
trellis.par.set(theme = canonical.theme(color = FALSE))
mykey <- simpleKey(levels(sim2$test), points = TRUE, lines = TRUE)
xyplot(power ~ diff | nlevels + pars, group = ~ test, data = sim2,
       subset = (parms=="extra+loading" & 
		 pars %in% c("Loading1", "All Loadings") & diff %% 0.5 == 0),
       type = "b", xlab = "Violation Magnitude", ylab = "Power", key = mykey, as.table = TRUE,
       strip = function(..., which.given, factor.levels){
	   if(which.given == 2){
	       strip.default(which.given, factor.levels = parlabs[c(1, 4)], ...)
	   } else {
	       strip.default(which.given, factor.levels = factor.levels, ...)
	   }
       })
@

@@

\begin{figure}
\caption{Simulated power curves for $\max \mathit{LM}_o$, $\mathit{WDM}_o$, and $\mathit{LM}_{uo}$ across three levels of the ordinal variable $m$ and measurement invariance 
violations of 0--4 standard errors (scaled by $\sqrt{n}$). The
parameter violating measurement invariance is $\phi_{12}$.  Panel
labels denote the parameter(s)  
being tested (top) and levels of the ordinal variable $m$ (bottom).}
\label{fig:sim24res}
<<sim24res, fig=TRUE, height=4, width=9, echo=FALSE>>=
trellis.par.set(theme = canonical.theme(color = FALSE))
mykey <- simpleKey(levels(sim2$test), points = TRUE, lines = TRUE)
xyplot(power ~ diff | nlevels, group = ~ test, data = sim2,
       subset = (parms=="extra+var" & 
		 pars %in% c("Covariance") & diff %% 0.5 == 0),
       type = "b", xlab = "Violation Magnitude", ylab = "Power", key = mykey, as.table = TRUE,
       strip = function(..., which.given, factor.levels){
	   if(which.given == 2){
	       strip.default(which.given, factor.levels = parlabs[c(2, 4:5)], ...)
	   } else {
	       strip.default(which.given, factor.levels = factor.levels, ...)
	   }
       })
@

\begin{figure}
\caption{Simulated power curves for $\max \mathit{LM}_o$, $\mathit{WDM}_o$, and $\mathit{LM}_{uo}$ across three levels of the ordinal variable $m$ and measurement invariance 
violations of 0--4 standard errors (scaled by $\sqrt{n}$). The
parameter violating measurement invariance is $\psi_{11}$.  Panel
labels denote the parameter(s)  
being tested (top) and levels of the ordinal variable $m$ (bottom).}
\label{fig:sim25res}
<<sim25res, fig=TRUE, height=7, width=9, echo=FALSE>>=
trellis.par.set(theme = canonical.theme(color = FALSE))
mykey <- simpleKey(levels(sim2$test), points = TRUE, lines = TRUE)
xyplot(power ~ diff | nlevels + pars, group = ~ test, data = sim2,
       subset = (parms == "extra+error" & 
		 pars %in% c("Error1", "All Errors") & diff %% 0.5 == 0),
       type = "b", xlab = "Violation Magnitude", ylab = "Power", key = mykey, as.table = TRUE,
       strip = function(..., which.given, factor.levels){
	   if(which.given == 2){
	       strip.default(which.given, factor.levels = parlabs[c(3,5)], ...)
	   } else {
	       strip.default(which.given, factor.levels = factor.levels, ...)
	   }
       })
@
